---
title: "사전인턴교육_R"
author: "Presenter: Yun-Gil Jun"
date: "November 26th 2016"
output: html_document
---

>###What is R?

- GPL(General public license: GNU): http://www.r-project.org/

- Comparison of Statistical Packages: http://en.wikipedia.org/wiki/Comparison_of_statistical_packages

>###How to get R

- NexR Corporation, Seoul: http://cran.nexr.com/

- Rstudio : http://www.rstudio.com/products/rstudio/download/

- MRAN : https://mran.microsoft.com/download/

- (for Text mining JAVA : http://www.oracle.com/technetwork/java/javase/downloads/index-jsp-138363.html )

>###1. Data Management

use the assignment operator to create new variables: <- 
Arthmetric Operations: +, -. *, /, ^
```
getwd()   # the current working directory
setwd()   # change to my directory
ls()      # list the objects in the current working workspace
example() # show an example of function
help()    # help about function
data()    # to see the availabe datasets

```

####data type : scalars, vectors(numerical, character, logical), metrics, arrays, dataframes, lists, factors
>###2. Examples
***
>####2.1 matrix
```{r}
a <- c(1, 2, 3, 4, 5, 6)
mymatrix <- matrix(a, nrow=2, ncol=3)
mymatrix

```
***
>####2.2 data.frame
```{r}
a <- c(1,2,3,4)                          # assign numeric vector
b <- c("red", "white", "red", "black")   # assign character vector
c <- c(TRUE, TRUE, TRUE, FALSE)          # assign logical vector
mydata <- data.frame(a,b,c)              # different colums(numeric, character, factor, etc)
mydata

```
***
>####2.3 Variable names
```{r}
names(mydata) <- c("number", "color", "passed")
mydata
```
***
>####2.4 Recall data
```{r}
mydata[2:4, 3]
mydata[c("number", "color")]
mydata$color  # recall variable data
```
***
>###3. Functions
***
####3.1 Function list of package
```{r}
# install.packages("plm")
# library(plm)
# help(package=plm)
```
***
>#### 3.2 Usefule Functions
```{}
length(mydata)              # number of elements
str(object)                 # structure of an object
class(object)               # class or type of an object
names(object)               # names
c(object, object, ...)      # combine objects into a vector
cbind(object, object, ...)  # combine objects as columns
rbind(object, object, ...)  # combine objects as rows
ls()                        # list current objects
rm()                        # delete an object
newobject <- edit(object)   # edit copy and save a new object
fix(object)                 # edit in place

```

***
>####3.3 Example
```{r}
str(str)
str(library)
str(help)
```
***
>###4. Importing Data
***
>####4.1 Text File
```{}
mydata <- read.table("c:/mydata.csv", header=TRUE, sep=",", row.names="id")
mydata <- read.csv("c:/mydata.csv", header=TRUE)
```
***
>####4.2 Excel File
```{}
library(xlsx)
mydata <- read.xlsx("c:/myexcel.xlsx", 1)  # first row contains variable names
mydata <- read.xlsx("c:/myexcel.xlsx", sheetName = "mysheet")
```
***
>####4.3 Getting Information on a Dataset
```{}
ls()               # list objects in the working environment
names(mydata)      # list the variables in mydata
str(mydata)        # list the structure of mydata
levels(mydata$v1)  # list levels of factor v1 in mydata
dim(object)        # dimensions of a object
class(object)      # class of an object (numeric, matrix, data frame, etc)
mydata             # print mydata
head(mydata, n=10) # print first 10 rows of mydata
tail(mydata, n=5)  # print last 5 rows of mydata

```
***
>###5. Data manipulation

***
>####5.1 Excluding Missing Values
```{r}
x <- c(1, 2, NA, 3)
mean(x)
mean(x, na.rm=TRUE)
```
***
>####5.2 Date Values
```{}
mydata[!complete.cases(mydata),]   # list rows of data that have missing values
newdata <- na.omit(mydata)         # create new dataset without missing data

```

```{}
mydates <- as.Date(c("2015-06-22", "2014-02-04" ))  # use. as.Date() to convert strings to dates
days <- mydates[1] - mydates[2]                     # number of days between 6/22/15 and 2/4/14

```
```{}
today <- Sys.Date()     # print today's date
format(today, format "%B %d %Y")
```
See help(as.Date)

***

>###Graph examples
```{r}
# library(ggplot2)
# qplot(diamonds$carat, diamonds$price)
# qplot(carat, price, data = diamonds)
# qplot(carat, price, data = diamonds, geom="point", color = clarity)
# qplot(carat, price, data = diamonds, geom=c("point", "smooth"), method=lm)
# qplot(carat,data = diamonds, geom="histogram")
# ggplot(data=diamonds, aes(x=carat, y=price)) + geom_point(aes(color=clarity)) + geom_smooth()
# ggplot(data=diamonds, aes(x=carat, y=price, color = clarity))+geom_point()+geom_smooth()

```
```{r}
library(rgl)
plot3d(iris$Petal.Width, iris$Sepal.Length, iris$Sepal.Width)
distMatrix <- as.matrix(dist(iris[,1:4]))
heatmap(distMatrix, main="heatmap")

```


